\documentclass[a4paper,12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{geometry}
\usepackage{hyperref}
\geometry{top=1in, bottom=1in, left=1in, right=1in}

\begin{document}

% Title Page
\begin{titlepage}
    \begin{center}
        \vspace*{1cm}
        
        \Huge
        \textbf{[Enter your Project Title Here]}
        
        \vspace{1.5cm}
        \Large
        \textbf{Submitted By:}\\
        [Student Name, Roll Number]
        
        % \vspace{2cm}
        % \Large
        % \textbf{Submitted To:}\\
        % [Instructor Name] \\
        % [Department Name, Institute Name]
        
        % \vspace{2cm}
        % \Large
        % \textbf{Date of Submission:} \\
        % [Enter Date Here]
    \end{center}
\end{titlepage}

% Aim
\section*{1. Aim}
Clearly state the goals of the project, e.g., simulation of a protocol, analysis of network performance, implementation of a networking concept, etc.

% Introduction
\section*{2. Introduction}
\begin{itemize}
    \item Brief overview of the project topic.
    \item Importance and relevance of the topic in computer networks.
    \item Description of the problem or scenario being addressed.
\end{itemize}

% System Design
\section*{3. System Design}
\subsection*{3.1 Architecture}
Describe the system architecture or topology used in the project. Include diagrams if applicable.

\subsection*{3.2 Protocol/Concept Details}
Describe the networking protocols, algorithms, or concepts used in the project.

\subsection*{3.3 Tools and Technologies}
List the software, hardware, and programming tools used.

% Implementation Details
\section*{4. Implementation Details}
\begin{itemize}
    \item Provide a detailed explanation of how the project was implemented.
    \item Include code snippets or configuration files if applicable.
    \item Describe the methodology followed step by step.
\end{itemize}

% Testing and Results
\section*{5. Testing and Results}
\begin{itemize}
    \item Describe the testing strategy and scenarios used to evaluate the project.
    \item Include any data collected during testing (e.g., packet loss, throughput, delay).
    \item Present results in the form of graphs, tables, or charts.
    \item Provide a brief analysis of the results.
\end{itemize}

% Discussions
\section*{6. Discussions}
\begin{itemize}
    \item Discuss any difficulties faced during the project.
    \item Mention any limitations or constraints in the implementation.
\end{itemize}

% Future Enhancements
\section*{7. Future Enhancements}
Suggest possible improvements or extensions to the project.

% References
\section*{8. References}
List all references in IEEE format, including textbooks, research papers, websites, or any other resources.

\end{document}
